Model Finding for (Co)recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-05 tex/main.tex
help tab completion ;)

A set of function definitions $\{ \varphi_1, \ldots, \varphi_n \}$ 
is \emph{admissible} (\emph{in $T$}) if $\varphi_1 \wedge \ldots \wedge \varphi_n$ is $T$-satisfiable.
For example, $\{ \forallf{\con{f}} \vec x.\;\, \con{f}( x ) \teq 0 \}$ is admissible,
whereas $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$ is not. 
Note that an admissible function definition need not specify a terminating function, e.g.
$\{ \forallf{\con{f}} x^\sortint.\;\, \con{f}( x ) \teq \con{f}( x - 1 ) \}$ or even $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) \}$ are admissible.
\ajr{revise}

\section{Model Finding for Recursive Functions in SMT}
\label{sec:model-finding-rec-fun}

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
A instantiation-based procedure is shown in~\cite{GeDeM-CAV-09} to be complete for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all occurrences of variables occur as direct subchildren of uninterpreted functions.
For example, the formula $\forall x\typ{\sortint}.\;\, \con{f}( x ) \teq g( x ) + 5$ 
is in the essentially uninterpreted fragment since all occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and $g$.
Other syntactic criteria are identified in this paper that extend this fragment slightly, including cases when variables occur as arguments of arithmetic predicates.
The techniques in~\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified formulas over uninterpreted types as well as types having a 
fixed finite interpretation (such as fixed-width bitvectors, datatype enumerations, etc.).
For example, finite model finding techniques can find a model for
the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, \neg x \teq y \vee \con{f}( x ) \teq \con{f}( y )$
where the uninterpreted type $\tau$ is interpreted as a finite set, and $\con{f}$ as injective finite map.

@@

{
\bibliographystyle{abbrv}
\bibliography{main}
}

>>>>

A set of function definitions $\{ \varphi_1, \ldots, \varphi_n \}$ 
is \emph{admissible} (\emph{in $T$}) if $\varphi_1 \wedge \ldots \wedge \varphi_n$ is $T$-satisfiable.
For example, $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq 0 \}$
and $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) \}$ are admissible,
whereas $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) + 1 \}$ is not.
\ajr{revise}

\jb{TODO: Jasmin: Identify fragments: terminating recursive functions, etc.}

%Terminating function specifications are always admissible, but also some
%nonterminating
%An admissible function definition need not specify a terminating function, e.g.
%$\{ \forallf{\con{f}} x^\sortint.\;\, \con{f}( x ) \teq \con{f}( x - 1 ) \}$ or even $\{ \forallf{\con{f}} x.\;\, \con{f}( x ) \teq \con{f}( x ) \}$ are admissible.

%\section{Model Finding for Recursive Functions in SMT}
\section{Model Finding for (Co)recursive Functions in SMT}
\label{sec:model-finding-rec-fun}

\jb{Break up big section into several? Or at least rename it to avoid repeating the
title. (What other subsections are planned?)}

Recent techniques~\cite{GeDeM-CAV-09, ReyEtAl-1-RR-13} 
have focused on finding models for quantified formulas in SMT.
\cite{GeDeM-CAV-09}
A instantiation-based procedure is shown in~ to be complete for formulas in the \emph{essentially uninterpreted} fragment.
This fragment is limited to universally quantified formulas where all occurrences of variables occur as direct subchildren of uninterpreted functions.
For example, the formula $\forall x\typ{\sortint}.\;\, \con{f}( x ) \teq g( x ) + 5$ 
is in the essentially uninterpreted fragment since all occurrences of $x$ occur beneath uninterpreted functions $\con{f}$ and $g$.
Other syntactic criteria are identified in this paper that extend this fragment slightly, including cases when variables occur as arguments of arithmetic predicates.
The techniques in~\cite{ReyEtAl-1-RR-13} can be used for finding finite models for quantified formulas over uninterpreted types as well as types having a 
fixed finite interpretation (such as fixed-width bitvectors, datatype enumerations, etc.).
For example, finite model finding techniques can find a model for
the formula $\forall x\typ{\tau} y\typ{\tau}.\;\, \neg x \teq y \vee \con{f}( x ) \teq \con{f}( y )$
where the uninterpreted type $\tau$ is interpreted as a finite set, and $\con{f}$ as injective finite map.

@@

{
\bibliographystyle{abbrv}
\bibliography{bib}
}
